---
title: "Airline Passenger Satisfaction - Random Forest Exploration"
author: "Leif Berg"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rsample)
library(randomForest)
library(tidymodels)
library(caret)
```
## About
This script is an exploration of using a random forest to train and classify satisfaction ratings of airline passengers. 

Data source: https://www.kaggle.com/datasets/teejmahal20/airline-passenger-satisfaction

## Setup

### Read in Data
Read in Training Data
```{r }
training_df <- read.csv("train.csv")
```
Read in Testing Data
```{r }
test_df <- read.csv("test.csv")
```
View structure of data
```{r}
str(training_df)
```
View first few rows of data
```{r}
head(training_df)
```

### Clean data
Remove any rows with NA (for simplicty)
#remove na values (any row with na)
```{r}
training_df <- na.omit(training_df)
test_df <- na.omit(test_df)
```

Ensure satisfaction is a factor
```{r}
training_df$satisfaction <- as.factor(training_df$satisfaction)
test_df$satisfaction <- as.factor(test_df$satisfaction)
```

## Model - Random Forest

Create Random Forest (limit items to ensure it finishes)
```{r}
rf <- randomForest(satisfaction ~., data=training_df[1:5000,])
rf
```

Create Predictions using random forest against test data
```{r}
pred <- predict(rf, test_df)
head(pred)
```

Create Confusion Matrix to display results 
```{r}
confusionMatrix(pred, test_df$satisfaction,positive='satisfied')